### 2024-10-09 esop25/examples.tex
checkpoint

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values $v$ are encoded as reconstructive
shares $v_1$ and $v_2$ held by each party with $v = v_1 \fplus v_2$.
We will follow the convention that shared values are identified by
strings $w$ and encoded as shares $\mx{w}{1}$ and $\mx{w}{2}$.  As for
YGC, ciphertypes reflect the confidentiality of GMW input encodings as
defined in the $\ttt{encodegmw}$ function in Figure \ref{fig-gmw}. No
programmer annotation is needed given the syntax of the function
body. More interestingly, the $\ttt{andgmw}$ gate definition shows how
a programmer hint can express the relevant confidentiality property of
the output share $\mx{z}{2}$ on client 2. The non-trivial equivalence
can be verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function
(as for $\ttt{encode}$).

@@

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values $v$ are encoded as reconstructive
shares $v_1$ and $v_2$ held by each party with $v = v_1 \fplus v_2$.
We will follow the convention that shared values are identified by
strings $w$ and encoded as shares $\mx{w}{1}$ and $\mx{w}{2}$.  As for
YGC, ciphertypes reflect the confidentiality of GMW input encodings as
defined in the $\ttt{encodegmw}$ function in Figure \ref{fig-gmw}. No
programmer annotation is needed given the syntax of the function
body. More interestingly, the $\ttt{andgmw}$ gate definition shows how
a programmer hint can express the relevant confidentiality property of
the output share $\mx{z}{2}$ on client 2. The non-trivial equivalence
can be verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function
(as for $\ttt{encode}$).

\subsubsection{Integrity Examples}

@@

We can capture both the preliminary distribution of Beaver triples and
BDOZ shares as a pre-processing predicate that establishes conditions
for initial memories (see Definition \ref{def-aprogtt}).  Here we
assume two input secrets $\elab{\secret{x}}{1}$ and
$\elab{\secret{y}}{2}$ and a single Beaver Triple to compute
$\elab{\secret{x}}{1} \ftimes \elab{\secret{y}}{2}$, but we can extend
this for additional gates.  As for GMW, we use
$\macgv{\mesg{w}}$\cnote{need to update this} to refer to
secret-shared values reconstructed with addition, but for BDOZ by
convention each share of $\macgv{\mesg{w}}$ is represented as
$\elab{\mesg{w\ttt{s}}}{\cid}$, the MAC of which is represented as a
$\elab{\mesg{w\ttt{m}}}{\cid}$ for all $\cid$, and each client holds a
key $\elab{\mesg{w\ttt{k}}}{\cid}$ for authentication of the other's
share.
$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fplus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fplus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$

$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$

$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$

$$
\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})
$$

>>>>

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar
to BDOZ as described in Section \ref{section-ipj}. In our definition
of GMW we use the convention that shared values $\macgv{w}$ are identified by
strings $w$ and encoded as shares $\mx{w}{1}$ and $\mx{w}{2}$.  As for
YGC, ciphertypes reflect the confidentiality of GMW input encodings as
defined in the $\ttt{encodegmw}$ function in Figure \ref{fig-gmw}. No
programmer annotation is needed given the syntax of the function
body. More interestingly, the $\ttt{andgmw}$ gate definition shows how
a programmer hint can express the relevant confidentiality property of
the output share $\mx{z}{2}$ on client 2. The non-trivial equivalence
can be verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function
(as for $\ttt{encode}$).

@@

@@

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{w}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{w}$.

The $\ttt{sum}$ function implements an addition gate. Note that this
is done non-interactively-- each party just sums its local shares
of the two values. The pre- and postcondition annotations
on $\ttt{sum}$ express the additive homomorphism associated
with this encryption scheme-- the sum of MACs of the input
shares is a valid MAC for the output share on each client,
which can be checked using the sum of keys of the input shares.

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which would subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given this, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $\fcod{a * b} = c$, unique per multiplication
gate, that are secret shared with clients during pre-processing.
In our encoding we assume the additional convention that each gate
output identifier distinguishes the Beaver triple, so for
example the share of the $a$ value for a gate $\ttt{"g1"}$
is identified by $\ttt{"g1as"}$, etc., and $\eqspre$ would
subsume the following constraints for the $a,b,c$ values of
gate $\ttt{"g1"}$.
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}
The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate.
